Assessing landscape N removal in coastal New England catchments using the

### 2023-09-06 manuscript/manuscript.Rmd
Add a couple of sentences about use in LISS fertilizer project.

N-Sink is a decision support tool and was created to be a useful, easy way for local land use managers to explore the relationship between land use and nitrogen pollution in their waters. Local decision-makers that have prioritized nitrogen mitigation in their long-term planning efforts can use this tool to help them better understand the potential impact of proposed development projects and zoning variances. Similarly, land trusts and other NGOs interested in N mitigation can use this tool to identify high priority areas for acquisition or restoration.

>>>>

N-Sink is a decision support tool and was created to be a useful, easy way for local land use managers to explore the relationship between land use and nitrogen pollution in their waters. Currently N-Sink is being used as an integral component in a project based in Long Island Sound, funded by the [Long Island Sound Study Research Fund](https://longislandsoundstudy.net/2022-research-project-descriptions/). The project is focused on targeting outreach on fertilizer use within the 43,560 km2 catchment. Local decision-makers that have prioritized nitrogen mitigation in their long-term planning efforts can use this tool to help them better understand the potential impact of proposed development projects and zoning variances. Similarly, land trusts and other NGOs interested in N mitigation can use this tool to identify high priority areas for acquisition or restoration.
